### 2017-02-06 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
Edits

Fig2A <- ggplot(dd3,
       aes(x = RTL,
           y = RTL1)) +
  ylab(expression('RTL ('*italic(t)*' + 1)')) + 
  xlab(expression('RTL ('*italic(t)*')')) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_text(size = 12),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
    geom_point(col = 'grey')+
  geom_abline(slope = 1,intercept = 0,lty = 2) +
  annotate('text',x = 0.3,y = 1.7,label = 'A')

@@

temp <- subset(dd3,TimeDiff < 4)
temp$MidAge <- (temp$Agemonths+temp$Agemonths1)/2
temp$Gainer <- ifelse(temp$DeltaRTL>0,1,0)

Fig2C <- ggplot(temp, aes(x = Agemonths,
           y = Gainer)) +
  ylab("Proportion gainers") + 
  xlab("Age") +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_text(size = 12),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
  geom_point(col = 'grey')+
  geom_count(alpha = 0.2)+
  geom_smooth()+
  annotate('text',x = -0.2,y = 1,label = 'C')

pdf('Figures/Figure 2.pdf',
    width = 7,
    height = 7,
    paper = 'a4')
multiplot(Fig2A,Fig2B,Fig2C,layout = matrix(c(1,2,3,3),nrow = 2,byrow = T))
dev.off()

>>>>

temp <- dd3
temp$Gainer <- ifelse(temp$DeltaRTL>0,"1","0")

Fig2A <- ggplot(temp,
       aes(x = RTL,
           y = RTL1,
           col = Gainer)) +
  ylab(expression('RTL ('*italic(t)*' + 1)')) + 
  xlab(expression('RTL ('*italic(t)*')')) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_text(size = 12),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
    geom_point()+
  geom_abline(slope = 1,intercept = 0,lty = 2) +
  scale_colour_manual(values = c("navy","red"))+
  annotate('text',x = 0.3,y = 1.7,label = 'A')

@@

Fig2C <- ggplot(temp, aes(x = Agemonths,
           y = DeltaRTL,col = Gainer)) +
  ylab("Proportion gainers") + 
  xlab("Age") +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_text(size = 12),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
  geom_point()+
  geom_smooth(col = "darkgrey",method = "lm",formula = y~log(x))+
  geom_abline(slope = 0,intercept = 0,lty = 2)+
  scale_colour_manual(values = c("navy","red"))+
  annotate('text',x = -0.2,y = 1,label = 'C')

Fig2D <- ddply()
ggplot(temp, aes(x = Agemonths,
           y = DeltaRTL,col = Gainer)) +
  ylab("Proportion gainers") + 
  xlab("Age") +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_text(size = 12),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
  geom_point()+
  geom_smooth(col = "darkgrey",method = "lm",formula = y~log(x))+
  geom_abline(slope = 0,intercept = 0,lty = 2)+
  scale_colour_manual(values = c("navy","red"))+
  annotate('text',x = -0.2,y = 1,label = 'C')

pdf('Figures/Figure 2.pdf',
    width = 7,
    height = 7,
    paper = 'a4')
multiplot(Fig2A,Fig2B,Fig2C,Fig2D,layout = matrix(c(1,2,3,4),nrow = 2,byrow = T))
dev.off()
